### 2022-03-09 src/text/3-applications-subsections/1D-analysis.tex
Adapt filenames and input commands

\section{Applications}
\label{sec:applications}

Gammapy can be used for a variety of science cases by different IACT experiments. (Refer to publications)
In this section, we show a non-exhaustive list of some typical analysis that be performed.

\subsection{Classical spectral analysis}
\label{ssec:1D-analysis}
\input{3-applications-subsections/3.1-1D-analysis}
\todo{Axel}
A classical spectral analysis using Reflected Regions. Showing flux points, reflected regions on the CTA galactic center data

\subsection{A 3D likelihood analysis}
\label{ssec:3D-analysis}
\input{3-applications-subsections/3.2-3D-analysis}
\todo{Laura}

Simulation of overlapping sources, 3D fitting, npred map, TS maps

\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
Ref:~\citep{Stewart2009}
\begin{figure*}[t]
        \centering
        \includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
        \caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
\end{figure*}

\subsection{Temporal analysis}
\label{ssec:temporal-analysis}
\input{3-applications-subsections/3.3-temporal-analysis}
\todo{Atreyee}
lightcurves and temporal models using the HESS PKS2155

\subsection{Multi instrument analysis}
\label{ssec:multi-instrument-analysis}
\input{3-applications-subsections/3.4-multi-instrument-analysis}
\todo{Cosimo Nigro}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysis} 
\end{figure*}

\subsection{Fitting using physical models}
\label{ssec:naima-analysis}
\input{3-applications-subsections/3.5-naima-analysis}
\todo{Cosimo}

Figure \ref{fig:multi_instrument_analysis}. Add explanation text.

\subsection{Population studies}
\label{ssec:population-studies}
\todo{Quentin Remy}

>>>>

\subsection{Classical spectral analysis}
\label{ssec:1D-analysis}
\todo{Axel}
A classical spectral analysis using Reflected Regions. Showing flux points, reflected regions on the CTA galactic center data

\begin{figure*}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/cta_galactic_center.pdf}
	\caption{CTA Galactic Center example}
	\label{fig:cta_galactic_center}
\end{figure*}

### 2022-03-09 src/text/3-applications-subsections/3D-analysis.tex
Adapt filenames and input commands

\section{Applications}
\label{sec:applications}

Gammapy can be used for a variety of science cases by different IACT experiments. (Refer to publications)
In this section, we show a non-exhaustive list of some typical analysis that be performed.

\subsection{Classical spectral analysis}
\label{ssec:1D-analysis}
\input{3-applications-subsections/3.1-1D-analysis}
\todo{Axel}
A classical spectral analysis using Reflected Regions. Showing flux points, reflected regions on the CTA galactic center data

\subsection{A 3D likelihood analysis}
\label{ssec:3D-analysis}
\input{3-applications-subsections/3.2-3D-analysis}
\todo{Laura}

@@

\subsection{Temporal analysis}
\label{ssec:temporal-analysis}
\input{3-applications-subsections/3.3-temporal-analysis}
\todo{Atreyee}
lightcurves and temporal models using the HESS PKS2155

\subsection{Multi instrument analysis}
\label{ssec:multi-instrument-analysis}
\input{3-applications-subsections/3.4-multi-instrument-analysis}
\todo{Cosimo Nigro}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysis} 
\end{figure*}

\subsection{Fitting using physical models}
\label{ssec:naima-analysis}
\input{3-applications-subsections/3.5-naima-analysis}
\todo{Cosimo}

Figure \ref{fig:multi_instrument_analysis}. Add explanation text.

\subsection{Population studies}
\label{ssec:population-studies}
\todo{Quentin Remy}

>>>>

\subsection{A 3D likelihood analysis}
\label{ssec:3D-analysis}

\todo{Laura}

@@

### 2022-03-09 src/text/3-applications-subsections/multi-instrument-analysis.tex
Adapt filenames and input commands

\section{Applications}
\label{sec:applications}

Gammapy can be used for a variety of science cases by different IACT experiments. (Refer to publications)
In this section, we show a non-exhaustive list of some typical analysis that be performed.

\subsection{Classical spectral analysis}
\label{ssec:1D-analysis}
\input{3-applications-subsections/3.1-1D-analysis}
\todo{Axel}
A classical spectral analysis using Reflected Regions. Showing flux points, reflected regions on the CTA galactic center data

\subsection{A 3D likelihood analysis}
\label{ssec:3D-analysis}
\input{3-applications-subsections/3.2-3D-analysis}
\todo{Laura}

Simulation of overlapping sources, 3D fitting, npred map, TS maps

\todo{What to do with } Figure~\ref{fig:fermi_ts_map} ?
Ref:~\citep{Stewart2009}
\begin{figure*}[t]
        \centering
        \includegraphics[width=1.\textwidth]{figures/fermi_ts_map.pdf}
        \caption{Fermi-LAT TS map in two energy bands} \label{fig:fermi_ts_map}
\end{figure*}

\subsection{Temporal analysis}
\label{ssec:temporal-analysis}
\input{3-applications-subsections/3.3-temporal-analysis}
\todo{Atreyee}
lightcurves and temporal models using the HESS PKS2155

\subsection{Multi instrument analysis}
\label{ssec:multi-instrument-analysis}
\input{3-applications-subsections/3.4-multi-instrument-analysis}
\todo{Cosimo Nigro}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysis} 
\end{figure*}

\subsection{Fitting using physical models}
\label{ssec:naima-analysis}
\input{3-applications-subsections/3.5-naima-analysis}
\todo{Cosimo}

Figure \ref{fig:multi_instrument_analysis}. Add explanation text.

\subsection{Population studies}
\label{ssec:population-studies}
\todo{Quentin Remy}

>>>>

\subsection{Multi instrument analysis}
\label{ssec:multi-instrument-analysis}
\todo{Cosimo Nigro}

\begin{figure*}[t]
	\sidecaption
	\includegraphics[width=0.666\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysis}
\end{figure*}

### 2022-03-09 src/text/3-applications.tex
Adapt filenames and input commands

Show some typical and advanced science cases, and refer to published papers

\subsection{Computing Flux points and significance maps}
\label{ssec:1D-3D-analysis}
\input{3.1-std-analysis}

- standard 1D and 3D analysis

See Figure~\ref{fig:fermi_ts_map}.

Ref:~\citep{Stewart2009}

\subsection{Temporal analysis}
\label{ssec:temporal-analysis}
\input{3.2-temporal}
lightcurves and temporal models

\subsection{Multi instrument analysis}
\label{ssec:multi-instrument-analysis}
\todo{Cosimo Nigro}
\begin{figure}[t]
	\centering
	\includegraphics[width=1.\textwidth]{figures/multi_instrument_analysis.pdf}
	\caption{A multi-instrument analysis of the Crab Nebula}
	\label{fig:multi_instrument_analysis} 
\end{figure*}

\subsection{Fitting using physical models}
\label{ssec:naima-models-analysis}
\todo{Cosimo}
\begin{figure*}[t]
(added section in the text requesting multi-insturment figure)

\end{figure}

\subsection{Population studies}
\label{ssec:population-studies}
\todo{Quentin Remy}

Talk about simulations here? Or open a new section

>>>>

Gammapy can be used for a variety of science cases by different IACT experiments. (Refer to publications)
In this section, we show a non-exhaustive list of some typical analysis that can be performed.
In general from the \gammapy side there is not limitation on which kind of analysis can be
done with wich instrument, however in practice it is limited by the availability of public data.

\input{text/3-applications-subsections/1D-analysis}
\input{text/3-applications-subsections/3D-analysis}
\input{text/3-applications-subsections/temporal-analysis}
\input{text/3-applications-subsections/multi-instrument-analysis}
\input{text/3-applications-subsections/sed-modelling-analysis}
\input{text/3-applications-subsections/population-studies}
